---
title: "Your title here"
date: "`r Sys.Date()`"
author: "Your group's SIDs (don't put your name, so that we can respect the anonymous marking policy)"
format: 
  html: 
    embed-resources: true # Creates a single HTML file as output
    code-fold: true # Code folding; allows you to show/hide code chunks
    code-tools: true # Includes a menu to download the code file 
    # code-tools are particularly important if you use inline R to 
    # improve the reproducibility of your report
table-of-contents: true # (Optional) Creates a table of contents
number-sections: true # (Optional) Puts numbers next to heading/subheadings
---

## Introduction

<See Assignment Briefing Page>

## Hypothesis tests

### Research Question 1
```{r}
#这个步骤在后期可以省略掉，主要是帮助自己去看有哪些categories
table(mydata$gender)
```

```{r, warning=FALSE}
mydata <- filter(mydata, gender == "Female"|gender== "Male")
#此步高度查重，可以加载开头，也可以放在这里，如果自己要用到的数据那一列本来就没有NA可以不用加
mydata = mydata %>% drop_na()
```

```{r}
mydata <- mydata %>% dplyr::filter(mark_goal > 50)
```

```{r}
summary(mydata$mark_goal[mydata$gender == "Female"])
summary(mydata$mark_goal[mydata$gender == "Male"])
```

Is student type associated with target grade expectations?

H A T P C 一会写在这个部分

### Research Question 2

Is there a difference in the average weekly paid work hours between A and B?\
这里只是举例给大家做演示～

### Research Question 3

-   Is there a difference in the target grade between A同学 and B同学？

-   HAPTC的完整步骤一会写这里

-   Assumption要重点去检查 1. Nomality 2. Equal varince
